Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya

### 2022-06-07 Manuscript_analyses.Rmd
figure format fix

```{r}
breed_res_endline$y$breed_adopter[breed_adopters]<-"Adopter"
breed_res_endline$y$breed_adopter[is.na(breed_res_endline$y$breed_adopter)]<-"Non-adopter"

@@

```{r}
nobull_res_endline$y$nobull_adopters<-NA
nobull_res_endline$y$nobull_adopters[nobull_adopters]<-"Adopter"
nobull_res_endline$y$nobull_adopters[is.na(nobull_res_endline$y$nobull_adopters)]<-"Non-adopter"

@@

```{r}
lessReplace_res_endline$y$lessReplace_adopters<-NA
lessReplace_res_endline$y$lessReplace_adopters[lessReplace_adopters]<-"Adopter"
lessReplace_res_endline$y$lessReplace_adopters[is.na(lessReplace_res_endline$y$lessReplace_adopters)]<-"Non-adopter"

>>>>

```{r, fig.dim = c(8, 8)}
breed_res_endline$y$breed_adopter[breed_adopters]<-"Adopter"
breed_res_endline$y$breed_adopter[is.na(breed_res_endline$y$breed_adopter)]<-"Non-adopter"

@@

```{r, fig.dim = c(8, 8)}
nobull_res_endline$y$nobull_adopters<-NA
nobull_res_endline$y$nobull_adopters[nobull_adopters]<-"Adopter"
nobull_res_endline$y$nobull_adopters[is.na(nobull_res_endline$y$nobull_adopters)]<-"Non-adopter"

@@

```{r, fig.dim = c(8, 8)}
lessReplace_res_endline$y$lessReplace_adopters<-NA
lessReplace_res_endline$y$lessReplace_adopters[lessReplace_adopters]<-"Adopter"
lessReplace_res_endline$y$lessReplace_adopters[is.na(lessReplace_res_endline$y$lessReplace_adopters)]<-"Non-adopter"
